A continental-scale analysis finds generalists, with large clutch size and residual brain mass, are the most urban-tolerant of birds

### 2018-05-21 ms.Rmd
added link for web-app

```{r Figure 3, echo=FALSE, fig.cap="A phylogenetic tree, based on Jetz et al. (2012) of the 477 bird species in the analysis, demonstrating the clustering of the urbanization index in regards to phylogeny. The tree demonstrates the urbanization index for each species in two ways: (1) coloring of the tips where dark red equates to a low urbanization index and dark blue equates to a high urbanization index, and (2) the size of the barplot portrayed for a species at its tip show the relative urbanization index. The urbanization index was taken as the median of the distribution for a species' average radiance values. Figure S3 shows a reference phylogenetic tree with the names of each tip displayed, and this link () provides an interactive visualization in order to easily identify each of the 477 species in the tree and their respective urbanization indices. For a full list of the 477 species included and their urbanization index see Appendix 4."}
knitr::include_graphics("finalFigs/Figure3.pdf")
```

>>>>

```{r Figure 3, echo=FALSE, fig.cap="A phylogenetic tree, based on Jetz et al. (2012) of the 477 bird species in the analysis, demonstrating the clustering of the urbanization index in regards to phylogeny. The tree demonstrates the urbanization index for each species in two ways: (1) coloring of the tips where dark red equates to a low urbanization index and dark blue equates to a high urbanization index, and (2) the size of the barplot portrayed for a species at its tip show the relative urbanization index. The urbanization index was taken as the median of the distribution for a species' average radiance values. Figure S3 shows a reference phylogenetic tree with the names of each tip displayed, and this link (https://johnwilshire.github.io/bird_urbanness_web_app/) provides an interactive visualization in order to easily identify each of the 477 species in the tree and their respective urbanization indices. For a full list of the 477 species included and their urbanization index see Appendix 4."}
knitr::include_graphics("finalFigs/Figure3.pdf")
```
